PyKE: Open source Python data analysis for NASA's Kepler, K2, and TESS missions

### 2018-01-20 paper/ms.tex
add example on folding a lightcurve

\documentclass{article}
\usepackage{amsmath, amssymb, mathtools, bm}
\usepackage{graphicx, graphics}
\DeclareMathOperator*{\argmin}{arg\,min}

@@

\section{Lightcurve Basics}
    \subsection{The \texttt{LightCurve} class}
        A \texttt{LightCurve} object can be instantiated by passing a \texttt{time}
        array, a \texttt{flux} array, and optionally a \texttt{flux\_err} array which
        accounts for uncertainties in the \texttt{flux} measurements.
        \begin{verbatim}
        from pyke.lightcurve import LightCurve
        lc = LightCurve(time, flux)
        \end{verbatim}

        Once instantiated, a \texttt{LightCurve} object provides methods such
        as:
        \begin{description}
            \item[\texttt{stitch}]: appends the attributes \texttt{flux},
                \texttt{time}, and \texttt{flux\_err} of other given
                \texttt{LighCurve} objects.
            \item[\texttt{flatten}]: applies a Savitzky-Golay filter to capture
                low frequency flux variations which can be then removed in order
                to aid transit detection algorithms.
            \item[\texttt{fold}]: folds a lightcurve at a given period and
                phase.
            \item[\texttt{bin}]: bins a lightcurve using a block mean or median.
            \item[\texttt{cdpp}]: computes the Combined Differential Photometric
                Precision (CDPP) metric, which is a proxy for the amount of
                scatter in the lightcurve signal.
            \item[\texttt{plot}]: plots a lightcurve in a user-friendly fashion.
        \end{description}

@@

        Therefore, one can, for example, perform the following series of operations
        in order to fold a lightcurve from the MAST archive
        \begin{verbatim}
        lc_file = KeplerLightCurveFile(path=PATH_TO_FILE)
        klc = lc_file.get_lightcurve("PDCSAP_FLUX").fold(period=10.8234)
        klc.plot()
        \end{verbatim}
        [use a real example here]

\section{Target Pixel File Basics}

@@

In the same fashion, we can apply cotrending basis vector correction to
\mathcal{K}\mathit{2} lightcurves.

@@

>>>>

\documentclass{article}
\usepackage{amsmath, amssymb, mathtools, bm}
\usepackage{graphicx, graphics}
\usepackage{array}
\DeclareMathOperator*{\argmin}{arg\,min}

@@

\section{Lightcurve Basics}
    \subsection{The \texttt{LightCurve} class}
        A \texttt{LightCurve} object can be instantiated by passing a \texttt{time}
        array, a \texttt{flux} array, and optionally a \texttt{flux\_err} array which
        accounts for uncertainties in the \texttt{flux} measurements, i.e.,
        \begin{verbatim}
        from pyke.lightcurve import LightCurve
        lc = LightCurve(time, flux)
        \end{verbatim}

        \texttt{LightCurve} object provides methods described in
        Table~(\ref{tab:methods})

        \begin{table}[!htb]
            \centering
            \caption{A subset of methods provided by the \texttt{LightCurve} class}
            \begin{tabular}{cp{7cm}}
                \hline
                \textbf{Method signature} & \textbf{Short description} \\
                \hline
                \texttt{stitch} & appends the attributes \texttt{flux},
                \texttt{time}, and \texttt{flux\_err} of other given
                \texttt{LighCurve} objects.\\
                \texttt{flatten} & applies a Savitzky-Golay filter to capture
                low frequency flux variations which can be then removed in order
                to aid transit detection algorithms.\\
                \texttt{fold} & folds a lightcurve at a given period and phase.\\
                \texttt{bin} &  bins a lightcurve using a block mean or median.\\
                \texttt{cdpp} &  computes the Combined Differential Photometric
                Precision (CDPP) metric, which is a proxy for the amount of
                scatter in the lightcurve signal. \\
                \texttt{plot} & displays a lightcurve.
            \end{tabular}
            \label{tab:methods}
        \end{table}

@@

        Therefore, one can, for example, perform the following series of operations
        in order to fold a lightcurve from the MAST archive
\begin{verbatim}
>>> lc_file = KeplerLightCurveFile("https://archive.stsci.edu/missions/kepler/"
... "lightcurves/0119/011904151/kplr011904151-2009350155506_llc.fits")
>>> klc = lc_file.get_lightcurve("PDCSAP_FLUX").fold(period=10.8234)
>>> klc.plot()
\end{verbatim}
        \begin{figure}[!htb]
            \centering
            \includegraphics[scale=.5]{figs/fold-lc.pdf}
            \caption{Folded lightcurve of target \texttt{KIC011904151} quarter 3, showing the
            transit signal of Kepler-10b.}
            \label{fig:fold-method}
        \end{figure}

\section{Target Pixel File Basics}
    \subsection{The \texttt{KeplerTargetPixelFile} class}
        A \texttt{KeplerTargetPixelFile} object can be instantiated
        by passing a \texttt{path} (URL or local) of a target pixel file.
        Optionally, the user the select to throw away frames that contain
        a specific flag by using the \texttt{quality\_bitmask} argument.

        \texttt{KeplerTargetPixelFile} offers a number of methods
        that range from getting raw aperture photometry lightcurves to
        data visualization.

        For instance, the method \texttt{plot} can be used to visualize a
        given frame, which are depicted in Fig.~\ref{}
\begin{verbatim}
import numpy as np
from pyke import KeplerTargetPixelFile
tpf = KeplerTargetPixelFile('kplr008462852-2011073133259_lpd-targ.fits.gz')
tpf.plot()
tpf.plot(aperture_mask=tpf.flux[0] > np.nanmean(tpf.flux[0]))
\end{verbatim}

        \begin{figure}[!htb]
            \includegraphics[scale=.4]{figs/tpf-plot.pdf}
            \includegraphics[scale=.4]{figs/tpf-plot-aperture.pdf}
            \caption{}
            \label{fig:plot-method}
        \end{figure}

@@

In the same fashion, we can apply cotrending basis vector correction to
$\mathcal{K}\mathit{2}$ lightcurves.

@@

\section{Acknowledgments}
PyKE is build on top of numerous packages that constitute the Python scientific
stack, more precisely, \texttt{numpy}, \texttt{scipy}, \texttt{matplotlib}, and
\texttt{astropy}.
